---
title: "Heap Onsite Project"
author: "Michael Mullarkey"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: no
geometry: margin=0.50in
---

```{r setup, include=FALSE, cache = FALSE}
require("knitr")
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, warning = FALSE, message = FALSE, include = TRUE)
```

# Packages

```{r}

library(tidyverse)
library(lubridate)
library(skimr)
library(showtext)
library(ggdist)
library(infer)
library(glue)

```

# Live Coding at Beginning

## Read in Data

```{r}

heap <- read_csv("heap-data-scientist-onsite.csv") %>% 
  mutate(
    across(
      where(is.character),
      factor
      )
    )

```

```{r}

# One row for each session_id, most important is converted

head(heap)

View(heap)

```

```{r}

heap %>% 
  mutate(month = month(session_time)) %>% 
  relocate(month, everything()) %>% 
  group_by(month) %>% 
  mutate(conversion_rate = mean(converted, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(month, .keep_all = TRUE) %>% 
  ggplot(aes(x = month, y = conversion_rate)) + 
  geom_line()


heap %>% 
  mutate(month = month(session_time)) %>% 
  relocate(month, everything()) %>% 
  group_by(month) %>% 
  count(converted)


prop.test(x = c(81, 120), n = c(343, 1514))

```

# Initial Notes

Overall plan: Let's go for low hanging fruit first and then try to get fancy

Low hanging fruit:

Let's do sessions by users visualization

Groupings with complete or nearly complete data that I don't have to engineer (can try pseudo R2, then fall back on more traditional stats if I have to)

We can do that with device type

We could also do that with number of marketing pages viewed as either >= 1 vs. 0

More complex ideas

Can try to create a function that generalizes across different numbers of groups for pseudo R2

Try to clean uo platform and do comparisons there

Do some KNN imputation to try to look at other groupings

```{r}

## Looking for insight not predictive power
## Statistical rigor is a tool not an outcome 

```

## Inspecting Data

```{r}

skim(heap)

```

```{r}

glimpse(heap)

```

## Visualizing Session Counts by User

```{r}

font_add_google("Oswald", "oswald")

showtext_auto()

heap %>% 
  group_by(user_id)  %>% 
  summarize(sessions = n()) %>% 
  ggplot(aes(x = sessions)) +
  geom_histogram(size = 3, fill = "#EE4860") +
  scale_x_log10() + 
  theme_dark() +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        text = element_text(color = "white", family = "oswald"),
        axis.text = element_text(color = "white", family = "oswald")) +
  labs(x = "Number of Sessions (Log Scale)",
       y = "Count",
       title = "Number of Sessions Per User is Hugely Left Skewed (Even on Log Scale)",
       subtitle = "We Only Get One Shot With Most Potential Users in this Sample")
  

```
## What's Our Average Conversion Rate by Session?

Not by user, since users can have multiple sessions

```{r}

heap %>% 
  count(converted) %>% 
   mutate(percent = (100 * n)/sum(n),
          converted = case_when(
            converted == FALSE ~ "Didn't Convert",
            converted == TRUE ~ "Converted"
          )) %>% 
   ggplot(aes(x = converted, y = n)) +
   geom_col(fill = "#2E124D") +
   coord_flip() +
   geom_text(aes(label = glue("{round(percent, 2)}%")), hjust = 1.1, color = "#EE4860", family = "oswald") +
   theme_dark() +
   theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        text = element_text(color = "white", family = "oswald"),
        axis.text = element_text(color = "white", family = "oswald")) +
   labs(x = "",
       y = "Number of Sessions",
       title = "See a 10.15% Conversion Rate Across All Sessions",
       subtitle = "Subsequent Comparisons Should Keep This Baseline in Mind")


```

## How Many Users Convert on Their First Visit Vs. Any Subsequent Visit?

My goal is to do this once, then try to facet by potential comparisons in a future plot

```{r}

heap %>% 
  group_by(user_id) %>% 
  arrange(session_time) %>% 
  summarize(convert_first = if_else(
    first(converted) == TRUE, "Yes",
    "No"
    )
  ) %>% 
  ungroup() %>% 
  count(convert_first = as.factor(convert_first)) %>%
  mutate(percent = (100 * n)/sum(n)) %>% 
  ggplot(aes(x = convert_first, y = n)) +
  geom_col(fill = "#2E124D") +
  coord_flip() +
  geom_text(aes(label = glue("{round(percent, 2)}%")), hjust = 1.1, color = "#EE4860", family = "oswald") +
  geom_hline(yintercept = 857, color = "dodgerblue1") +
  annotate(geom = "text", x = 2, y = 1800, label = "Sample Conversion Rate\n10.15%", color = "dodgerblue1", family = "oswald") +
  theme_dark() +
   theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        text = element_text(color = "white", family = "oswald"),
        axis.text = element_text(color = "white", family = "oswald")) +
   labs(x = "",
       y = "Number of Sessions",
       title = "See a 10.15% Conversion Rate Across All Sessions",
       subtitle = "Subsequent Comparisons Should Keep This Baseline in Mind")

heap %>% 
  group_by(user_id) %>% 
  arrange(session_time) %>% 
  summarize(convert_first = if_else(
    row_number() == 1 & converted == TRUE, "Yes",
    "No"
    )
  ) %>% 
  count(user_id) %>% 
  arrange(desc(n))

```

## Formal Comparison of Proportion of Sessions That Convert First Session Vs. Any Subseqent Session by User

```{r}

heap %>% 
  group_by(user_id) %>% 
  arrange(session_time) %>% 
  summarize(convert_first = if_else(
    row_number() == 1 & converted == TRUE, "Yes",
    "No"
    )
  ) %>% 
  ungroup() %>% 
  count(convert_first = as.factor(convert_first)) %>% 
  prop_test(convert_first ~ NULL, success = "Yes", p = .1015, z = TRUE) %>% 
  print()

```
## Let's Iterate Over This Plot Across Multiple Kinds of Comparisons

# Let's See What Comparisons are Feasible Given Timeline

Can clean up platform, country, browser, utm_source, n_marketing_pages_viewed_before

```{r}

fac_vars <- heap %>% 
  select(where(is.factor)) %>% 
  names()

map(fac_vars, ~{
  heap %>% 
    count(.data[[.x]]) %>% 
    arrange(desc(n))
})

```

# Let's Clean Up These Grouping Variables

```{r}

heap_grp <- heap %>% 
  mutate(across(where(is.factor),as.character),
    platform = case_when(
    str_detect(platform, "Android") == TRUE ~ "Android",
    str_detect(platform, "Chrome") == TRUE ~"Chrome",
    str_detect(platform, "Firefox") == TRUE ~ "Firefox",
    str_detect(platform, "iOS") == TRUE ~ "iOS",
    str_detect(platform, "Mac OS") == TRUE ~ "Mac OS",
    str_detect(platform, "Windows") == TRUE ~ "Windows",
    platform == "Linux" | str_detect(platform, "Ubuntu") == TRUE ~ "Linux",
    TRUE ~ platform
    ),
    country = case_when(
      country == "United States" ~ "United States",
      is.na(country) ~ NA_character_,
      TRUE ~ "Outside US"
    ),
    marketing_viewed = case_when(
      n_marketing_pages_viewed_before == 0 ~ "None",
      n_marketing_pages_viewed_before == 1 ~ "One",
      n_marketing_pages_viewed_before >= 2 ~ "More Than One",
    )
  )

heap %>% 
  count(n_marketing_pages_viewed_before)

heap_grp %>% 
  count(country)

heap_grp %>% 
  count(marketing_viewed)

```

```{r}

## Attempt to pivot

heap_grp %>% 
  select(platform, country, marketing_viewed, converted) %>% 
  pivot_longer(
    -converted,
    names_to = "group_var",
    values_to = "value"
  ) %>%
  group_by(group_var, value) %>% 
  count(converted) %>% 
  ungroup() %>% 
  mutate(percent = (100 * n)/sum(n)) %>%
  ggplot(aes(x = value, y = percent)) +
  geom_col(fill = "#2E124D") +
  coord_flip() +
  facet_wrap(~group_var, ncol = 1, scales = "free") +
  geom_text(aes(label = glue("{round(percent, 2)}%")), hjust = 1.1, color = "#EE4860", family = "oswald") +
  # geom_hline(yintercept = 857, color = "dodgerblue1") +
  # annotate(geom = "text", x = 2, y = 1800, label = "Sample Conversion Rate\n10.15%", color = "dodgerblue1", family = "oswald") +
  theme_dark() +
   theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        text = element_text(color = "white", family = "oswald"),
        axis.text = element_text(color = "white", family = "oswald")) +
   labs(x = "",
       y = "",
       title = "",
       subtitle = "")

```

```{r}

## Attempt to map through for visualization

grp_vars <- c("platform", "country", "marketing_viewed")

map(grp_vars, ~{
  
  heap_grp %>%
  group_by(.data[[.x]]) %>%
  summarize(converted = mean(converted, na.rm = TRUE),
            num_sessions = n()) %>% 
  filter(num_sessions > 100) %>% 
  # mutate(
  #       # percent = (100 * n)/sum(n),
  #        converted = factor(case_when(
  #           converted == FALSE ~ "Didn't Convert",
  #           converted == TRUE ~ "Converted"
  #         ))) %>%
  ggplot(aes(x = .data[[.x]], y = converted)) +
  geom_col(fill = "#2E124D") +
  coord_flip() +
  geom_text(aes(label = glue("{round(converted*100, 2)}%")), hjust = 1.1, color = "#EE4860", family = "oswald") +
  # geom_hline(yintercept = 857, color = "dodgerblue1") +
  # annotate(geom = "text", x = 2, y = 1800, label = "Sample Conversion Rate\n10.15%", color = "dodgerblue1", family = "oswald") +
  theme_dark() +
   theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        text = element_text(color = "white", family = "oswald"),
        axis.text = element_text(color = "white", family = "oswald")) +
   labs(x = "",
       y = "",
       title = "",
       subtitle = "")
  
})



heap_grp %>%
  group_by(country) %>%
  summarize(converted = mean(converted, na.rm = TRUE),
            num_sessions = n()) %>% 
  filter(num_sessions > 100) %>% 
  # mutate(
  #       # percent = (100 * n)/sum(n),
  #        converted = factor(case_when(
  #           converted == FALSE ~ "Didn't Convert",
  #           converted == TRUE ~ "Converted"
  #         ))) %>%
  ggplot(aes(x = country, y = converted, fill = num_sessions)) +
  geom_col() +
  coord_flip() +
  geom_text(aes(label = glue("{round(converted*100, 2)}%")), hjust = 1.1, color = "#EE4860", family = "oswald") +
  # geom_hline(yintercept = 857, color = "dodgerblue1") +
  # annotate(geom = "text", x = 2, y = 1800, label = "Sample Conversion Rate\n10.15%", color = "dodgerblue1", family = "oswald") +
  theme_dark() +
   theme(legend.position = "top",
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        text = element_text(color = "white", family = "oswald"),
        axis.text = element_text(color = "white", family = "oswald")) +
   labs(x = "",
       y = "",
       title = "",
       subtitle = "")

```
## Attempt to Do Formal Tests

```{r}

heap %>% 
  group_by(platform) %>% 
  arrange(session_time) %>% 
  count(converted) %>% 
  prop_test(convert_first ~ NULL, success = "Yes", p = .1015, z = TRUE) %>% 
  print()

p.adjust()

```










