---
title: "Heap Onsite Project"
author: "Michael Mullarkey"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: no
geometry: margin=0.50in
---

```{r setup, include=FALSE, cache = FALSE}
require("knitr")
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, warning = FALSE, message = FALSE, include = TRUE)
```

# Packages

```{r}

library(tidyverse)
library(lubridate)
library(skimr)
library(showtext)
library(ggdist)

```

# Live Coding at Beginning

## Read in Data

```{r}

heap <- read_csv("heap-data-scientist-onsite.csv") %>% 
  mutate(
    across(
      where(is.character),
      factor
      )
    )

```

```{r}

# One row for each session_id, most important is converted

head(heap)

View(heap)

```

```{r}

heap %>% 
  mutate(month = month(session_time)) %>% 
  relocate(month, everything()) %>% 
  group_by(month) %>% 
  mutate(conversion_rate = mean(converted, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(month, .keep_all = TRUE) %>% 
  ggplot(aes(x = month, y = conversion_rate)) + 
  geom_line()


heap %>% 
  mutate(month = month(session_time)) %>% 
  relocate(month, everything()) %>% 
  group_by(month) %>% 
  count(converted)


prop.test(x = c(81, 120), n = c(343, 1514))

```

# Initial Notes

Overall plan: Let's go for low hanging fruit first and then try to get fancy

Low hanging fruit:

Let's do sessions by users visualization

Groupings with complete or nearly complete data that I don't have to engineer (can try pseudo R2, then fall back on more traditional stats if I have to)

More complex ideas

Do some KNN imputation to try to look at other groupings

```{r}

## Looking for insight not predictive power
## Statistical rigor is a tool not an outcome 

```

## Inspecting Data

```{r}

skim(heap)

```

```{r}

glimpse(heap)

```


## Visualizing Session Counts by User

```{r}

font_add_google("Oswald", "oswald")

showtext_auto()

heap %>% 
  group_by(user_id)  %>% 
  summarize(sessions = n()) %>% 
  ggplot(aes(x = sessions)) +
  geom_histogram(size = 3, fill = "#2E124D") +
  scale_x_log10() + 
  theme_dark() +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        text = element_text(color = "white", family = "oswald"),
        axis.text = element_text(color = "white", family = "oswald")) +
  labs(x = "Number of Sessions (Log Scale)",
       y = "Count",
       title = "Number of Sessions Per User is Hugely Left Skewed (Even on Log Scale)",
       subtitle = "We Only Get One Shot With Most Potential Users in this Sample")
  

```


















